Toxic Code Snippets on Stack Overflow

### 2018-05-15 cloverflow-tse/cloverflow.tex
Latest update with many improvements.

\begin{boxquote}
	To answer RQ2, we found more than half (53\%) of Qualitas projects to share
	similar code with Stack Overflow code snippets. In the manually confirmed 
	data set of 2,289 clone pairs, we found 2,076 pairs as true positives which 
	account for 59 Qualitas projects and
	443 Stack Overflow code snippets.
\end{boxquote}

@@

>>>>

\begin{boxquote}
	To answer RQ2, we found 2,076 manually confirmed clone pairs between 443 Stack Overflow code snippets
	and 59 Qualitas proejcts. 
	%After the manual confirmation, 2,076 pairs as true positives, i.e.~
	%they are manually confirmed as clones, which 
	%account for 59 Qualitas projects and
	%443 Stack Overflow code snippets.
\end{boxquote}

@@

\begin{table}
\centering
\label{tab:license_github}
\caption{Clones of the 214 missing-license code snippets in 131,703 GitHub projects}
\begin{tabular}{lrr}
	\toprule
	No. of stars & Qualitas & Other Projects \\
	\midrule
	29,540 to 10 stars & 71 & 1,836 \\
	9 to 5 stars & 0 & 739 \\
	4 to 1 stars & 19 & 4,541 \\
	\midrule
	Total & 90 & 7,116 \\
	\bottomrule
\end{tabular}
\end{table}
